MCC PRefere

### 2018-05-31 stats/mcc_pref.kids.Rmd
model comparisons update

p1 <- d %>%
  filter(trial_type == "test") %>%
  group_by(change,age, id) %>%
  summarise(correct = mean(correct))

@@

data_cg <- d%>%
  filter(trial_type == "test")%>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent))

>>>>

p1 <- d %>%
  filter(trial_type == "test") %>%
  group_by(change, id) %>%
  summarise(correct = mean(correct))

@@

data_cg <- d%>%
  filter(trial_type == "test")%>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent),
         age = scale(age))
